---
title: "Xu_Jingwen_AssignmentV"
subtitle: "GitHub and the ticketmaster.com API"
author: "submitted by Jingwen Xu (Student ID: 5631584)"
date: "February 14 2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

I discussed together with Martin Scheerer (ID: 5631373), Michael Lyubkin (ID: 4168485), Lana Kern (ID: 5395819) and Anton Höhl (ID: 5637078). I assure that my assignment conform to the rules and guidelines in the *Code of Conduct*.

## General Set-up
First of all, I clear the workspace and install the packages that be needed and load the packages.

```{r set_up, message=FALSE}

rm(list = ls())  # clear the workspace

# check if the packages has been installed; if not, then install
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("xml2")) install.packages("xml2")
if (!require("httr")) install.packages("httr")
if (!require("jsonlite")) install.packages("jsonlite")
if (!require("rlist")) install.packages("rlist")
if (!require("ggplot2")) install.packages("ggplot2")

# load packages
library(tidyverse)
library(xml2)
library(httr)
library(jsonlite)
library(rlist)
library(ggplot2)

```
## Exercise 1: 
The hyperlink is  <https://github.com/NeverJW/AssignmentV-DSPM.git>

## Exercise 2: Getting to know the API

## Exercise 3: Interacting with the API - the basics
### Search for event venues in Germany
``` {r Ex3_1, message=FALSE}

source("API_key.R")
res_venues <-
  GET(
    "https://app.ticketmaster.com/discovery/v2/venues?",
    query = list(
      apikey = API_key,
      locale = "*",
      countryCode   = "DE"
    )
  )
names(res_venues)
status_code(res_venues)
content <- fromJSON(content(res_venues, as = "text"))

```

### Extract the 7 columns and 20 rows data frame
```{r Ex3_2, message=FALSE}

venue_data <- as.data.frame(content[["_embedded"]][["venues"]])
venue_data <-
  venue_data[c("name", "city", "postalCode", "address", "url", "location")]
venue_data <-
  venue_data %>% mutate(
    city = city$name,
    address = address$line1,
    longitude = location$longitude,
    latitude = location$latitude,
    location = NULL
  )

glimpse(venue_data)

```

## Exercise 4: Interacting with the API - advanced
```{r ex4, message=FALSE}

# total results
n <- as.numeric(content[["page"]][["totalElements"]])

# Number of complete pages:
pages <- floor(n / 20) - 1 # because the page start from 0

# Number of entries on the last incomplete page:
remainder <- n - 20 * floor(n / 20)

# create a empty dataframe
# We initiate a dataframe in the correct dimensions to speed up our loop:
venue_df <- tibble(
  name  = character(n),
  city = character(n),
  postalCode = character(n),
  address   = character(n),
  url = character(n),
  longitude = character(n),
  latitude = character(n)
)


for (i in 0:23) {
  res_venues <-
    GET(
      "https://app.ticketmaster.com/discovery/v2/venues?",
      query = list(
        apikey = API_key,
        locale = "*",
        size = "500",
        countryCode   = "DE",
        page   = i
      )
    )
  
  content <- fromJSON(content(res_venues, as = "text"))
  # We gradually fill our dataframe page by page (lines 1-20 in the first  iteration, lines 21-40 in the second iteration, ...):
  venue_df[(500 * (i + 1) - 499):(500 * (i + 1)), c(1, 3, 5)] <-
    as.data.frame(content[["_embedded"]][["venues"]][c("name", "postalCode", "url")])
  venue_df[(500 * (i + 1) - 499):(500 * (i + 1)), 2] <-
    as.data.frame(content[["_embedded"]][["venues"]][["city"]][["name"]])
  venue_df[(500 * (i + 1) - 499):(500 * (i + 1)), 4] <-
    content[["_embedded"]][["venues"]][["address"]][["line1"]]
  
  if (is.null(content[["_embedded"]][["venues"]][["location"]][["longitude"]]) == TRUE) {
    venue_df[(500 * (i + 1) - 499):(500 * (i + 1)), 6] <- NA
  }
  else {
    venue_df[(500 * (i + 1) - 499):(500 * (i + 1)), 6] <-
      content[["_embedded"]][["venues"]][["location"]][["longitude"]]
  }
  if (is.null(content[["_embedded"]][["venues"]][["location"]][["latitude"]]) == TRUE) {
    venue_df[(500 * (i + 1) - 499):(500 * (i + 1)), 7] <- NA
  }
  else {
    venue_df[(500 * (i + 1) - 499):(500 * (i + 1)), 7] <-
      content[["_embedded"]][["venues"]][["location"]][["latitude"]]
  }
  Sys.sleep(10)
}

# The last page is incomplete, hence we add it manually outside
# the loop, as in this particular case, the loop would cause problems otherwise:
i <- i + 1
res_venues <-
  GET(
    "https://app.ticketmaster.com/discovery/v2/venues?",
    query = list(
      apikey = API_key,
      locale = "*",
      size = "500",
      countryCode   = "DE",
      page   = i
    )
  )

content <- fromJSON(content(res_venues, as = "text"))
# We gradually fill our dataframe page by page (lines 1-20 in the first  iteration, lines 21-40 in the second iteration, ...):
venue_df[(500 * (i + 1) - 499):(n), c(1, 3, 5)] <-
  as.data.frame(content[["_embedded"]][["venues"]][c("name", "postalCode", "url")])
venue_df[(500 * (i + 1) - 499):(n), 2] <-
  as.data.frame(content[["_embedded"]][["venues"]][["city"]][["name"]])
venue_df[(500 * (i + 1) - 499):(n), 4] <-
  content[["_embedded"]][["venues"]][["address"]][["line1"]]
venue_df[(500 * (i + 1) - 499):(n), 6] <-
  content[["_embedded"]][["venues"]][["location"]][["longitude"]]
venue_df[(500 * (i + 1) - 499):(n), 7] <-
  content[["_embedded"]][["venues"]][["location"]][["latitude"]]


glimpse(venue_df)
```

## Exercise 5: Visualizing the extracted data
```{r ex_5}
# set NA where the value of longitude and latitude outside the border range

venue_df_map <- venue_df
venue_df_map$longitude <- as.numeric(venue_df_map$longitude)
venue_df_map$latitude <- as.numeric(venue_df_map$latitude)


venue_df_map$longitude[venue_df_map$longitude < 5.866944] <- NA
venue_df_map$longitude[venue_df_map$longitude > 15.043611] <- NA

venue_df_map$latitude[venue_df_map$latitude < 47.271679] <- NA
venue_df_map$latitude[venue_df_map$latitude > 55.0846] <- NA


ggplot(venue_df_map, aes(x = as.numeric(longitude), y = as.numeric(latitude))) +
  geom_polygon(
    aes(x = long, y = lat, group = group),
    data = map_data("world", region = "Germany"),
    fill = "grey90",
    color = "black"
  ) + geom_point(color = "blue",
                 na.rm = TRUE,
                 alpha = 0.5) +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
  theme(
    title = element_text(size = 8, face = 'bold') +
      coord_cartesian(
        xlim = c(5.866944 - .2, 15.043611 + .2),
        ylim = c(47.271679 - .2, 55.0846 + .2)
      ),
    plot.caption = element_text(face = "italic")
  )


```

## Exercise 6: Event locations in other countries

```{r Ex_6}

```






