---
title: "Xu_Jingwen_AssignmentV"
subtitle: "GitHub and the ticketmaster.com API"
author: "submitted by Jingwen Xu (Student ID: 5631584)"
date: "February 14 2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

I discussed together with Martin Scheerer (ID: 5631373), Michael Lyubkin (ID: 4168485), Lana Kern (ID: 5395819) and Anton Höhl (ID: 5637078). I assure that my assignment conform to the rules and guidelines in the *Code of Conduct*.

## General Set-up
First of all, I clear the workspace and install the packages that be needed and load the packages.

```{r set_up, message=FALSE}

rm(list = ls())  # clear the workspace

# check if the packages has been installed; if not, then install
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("xml2")) install.packages("xml2")
if (!require("httr")) install.packages("httr")

# load packages
library(tidyverse)
library(xml2)
library(httr)

```
## Exercise 1: 
The hyperlink is  <https://github.com/NeverJW/AssignmentV-DSPM.git>

## Exercise 2: Getting to know the API

## Exercise 3: Interacting with the API - the basics

## Exercise 4: Interacting with the API - advanced

## Exercise 5: Visualizing the extracted data

## Exercise 6: Event locations in other countries







